%!TEX root = ../dissertation.tex
% the acknowledgments section

\newthought{First and foremost,} I would like to express my deepest gratitude to my advisor, Nico D\"ottling, for his steadfast mentorship and advice, which guided me in my research and cultivated my professional growth. His insightful feedback, patience, and intellectual rigor have been instrumental in shaping this work and my academic career.

I also wish to express my sincere appreciation to Antoine Joux, Markus Bl\"aser, and my exceptional co-referee, Geoffroy Couteau. Their willingness to review my work despite their own demanding schedules is something I deeply appreciate. 
%Their interest in my research has been a significant motivation for me. 
% I also wish to express my sincere appreciation to my exceptional co-referee, Geoffroy Couteau, whose willingness to participate in the review process and his interest in my work have immensely contributed to my motivation in this endeavor. 

Special thanks go to my collaborators, particularly Pedro Branco, and Sri Aravinda Krishman, with whom I had the privilege of collaborating on several research projects. Their unique perspectives, insightful contributions, and dedication to high-quality research have significantly enriched my work and personal growth as a researcher.
I also wish to acknowledge my colleagues Jesko Dujmovic, Chuanwei Lin, and Nabil Alkeilani Alkadri, who created an inspiring work environment and provided much-needed support and motivation throughout this journey. Their camaraderie, intellectual discussions, and shared advice were invaluable in the completion of this thesis.

Lastly, I would like to extend my heartfelt gratitude to my parents, whose unwavering belief in my abilities, constant support, and endless encouragement have been the cornerstone of my resilience during the entirety of this scholarly pursuit. Thank you for being my source of strength and positivity.
%$\acute{\text{c}}$